MSHS COVID-19 Vaccinations

### 2021-08-31 Empl_Arrival_Tracking.Rmd
Update markdown file for daily employee vaccine tracking. Update top level file to reflect changes to automated report.

@@

empl_arr_df <- employee_arr %>%
  filter(PatientType == "Employee" &
           ApptDate >= employee_arr_start_date) %>%
  mutate(PatientType = NULL)

>>>>

# MSHS color scheme
sinai_colors <- c("#221f72", "#C4C3EF",
                  "#00AEEF", "#B3EBFF",
                  "#D80B8C", "#FBB6E2",
                  "#7F7F7F")

@@

empl_arr_df <- employee_arr %>%
  filter(PatientType == "Employee" &
           ApptDate >= empl_arr_start_date) %>%
  mutate(PatientType = NULL)
